Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-20 writeup/gz_hubble_data.tex
Feedback from Boris, espec. on Figure 12

Figure~\ref{fig:comparisons} shows the proportion of galaxies as split by their
automated/expert visual morphologies for each of the six catalogs matched to
GZH. The relation between GZH and the automated/expert morphologies is shown to
vary significantly for different surveys --- this could be due to intrinsic
differences in the galaxies, in the techniques used to measure morphology, or
both. The distribution of \fbest{} for AEGIS galaxies is essentially flat for
spirals, showing almost no difference in proportion at the highest and lowest
ends. Early-type galaxies are at their highest proportion at \fbest$\sim0$, but
constitute at most only 40\% of galaxies. In contrast, GOODS galaxies at low
\fbest{} are dominated by early-types, although spiral and irregular galaxies
have comparable sizes as low as \fbest$\sim0.2$. In GEMS galaxies, the impact
of irregular or peculiar galaxies is not measured; splitting on $n=2.5$ gives
an essentially flat proportion of ellipticals to spirals at \fbest$>0.3$.
Visual inspection of images of galaxies where both \fbest{} and $n$ are high
show that the majority are obvious spirals but with prominent bulges,
indicating that the single-component \sersic{} fit is likely choosing too small
of an effective radius and missing the extended disk structure for a large
population of galaxies.

>>>>

Figure~\ref{fig:comparisons} shows the proportion of galaxies as split by their
automated/expert visual morphologies for each of the six catalogs matched to
GZH. The relation between GZH and the automated/expert morphologies is shown to
vary significantly for different surveys --- this could be due to intrinsic
differences in the galaxies, in the techniques used to measure morphology, or
both. The distribution of \fbest{} for AEGIS galaxies is essentially flat for
spirals, showing almost no difference in proportion at the highest and lowest
ends. Early-type galaxies are at their highest proportion at \fbest$\sim0$, but
constitute at most only 40\% of galaxies. In contrast, GOODS galaxies at low
\fbest{} are dominated by early-types, although spiral and irregular galaxies
have comparable sizes as low as \fbest$\sim0.2$.

In GEMS galaxies, the impact of irregular or peculiar galaxies is not measured;
splitting on $n=2.5$ gives an essentially flat proportion of ellipticals to
spirals at \fbest$>0.3$.  Visual inspection of images of galaxies where both
\fbest{} and $n$ are high show that the majority are obvious spirals but with
prominent bulges, indicating that the single-component \sersic{} fit is likely
choosing too small of an effective radius and missing the extended disk
structure for a large population of galaxies. This is a known issue with using
$n$ as a standalone measure of galaxy morphology -- it is relatively common,
for example, to measure high $n$ for an object with an exponential disk but a
central cusp in the light profile (eg, due to an AGN, cluster, foreground
star, noise, etc).
